Fusion Moves for Correlation Clustering

### 2014-11-12 paper/egpaper_for_review.tex
removed some links and improved proposal generation
woring oon proof

A further difference is how we efferently calculate the correlation clustering fusion move and how we generate proposals.
Both will be discussed next.

@@

\subsection{Fast Optimization of CCFusion Moves} \label{sec:fast_optimization}

Eq.~\ref{eq:fusion_move_a} can be solved efficiently, since 
we can work on a coarser graph, where all nodes which are connected
via must-link constraints are merged into single nodes.
This coarser graph is constructed by contracting all must-link edges
(see Fig.~\ref{fig:move_graph}).

\begin{definition}\emph{(Contradicted Graph)}
Given a weighted graph $G=V,E,w)$ segmentation of $G$ given by $y\in P(G)$,
we denote by $S: V \to \mathbb{N}$ a mapping from the nodes to the segments.
We define the contradiction of graph $G_y=(V_y,E_y, \bar{w})$
by $V_y=\{S(v)|v\in V\}$, $E_y=\{S(u)S(v)|uv\in E\}$, and 
$\forall \bar{u}\bar{v}\in E_y: \bar{w}_{\bar{u}\bar{v}}=\sum_{uv\in E, S(u)=\bar{u},S(v)=\bar{v}}w_{uv}$ 
\end{definition}

\begin{definition}\emph{(Back Projection)}
Given a segmentation $\bar{y}$ of a contradicted graph $G_y=(V_y,E_y)$.
We define the back projection $\rho^G$ from $\bar{y}$ to a segmentation of original graph  $G=(V,E)$
by 
\begin{align}
\rho^G_{uv}(\bar{y})=\left\{ 
\begin{array}{ll}
\bar{y}_{S(u)S(v)}& \textrm{ if }S(u) \neq S(v)\\
0                & \textrm{ else}
\end{array}
\right.
\end{align}
\end{definition}

\begin{theorem}[Equivalence]
The optimal multicut $\bar{y}^*$ on the contracted graph $G_y$
is equivalent to the optimal multicut $y^*$ in the original graph $G$ 
with additional must link constraints ($y^* \leq y$).
%
\begin{proof}
Since $y^*$ fulfills all  must link constraints, we have  $y^*\cdot w = \rho^{-1}_y(y^*)\cdot \bar{w}$.
Consequently, $y^*\cdot w = \rho_y(\bar{y}) \cdot w$ and  $\rho^{-1}_y(y^*)\cdot \bar{w}= \bar{y}\cdot\bar{w}$.
\end{proof}
%
\end{theorem}

>>>>

A further difference is how we efferently calculate the correlation clustering fusion move and how we generate proposals.
Both will be discussed next. The overall framework is sketched in Fig.~\ref{fig:move_graph}.

@@

\subsection{Fast Optimization of CCFusion Moves} \label{sec:fast_optimization}
In general the auxiliary fusion problem~\ref{eq:fusion_move_a} is still NP-hard.
However, many variables have been fixed to be zero and we can reformulate~\ref{eq:fusion_move_a}
into a correlation clustering problem on a coarser graph, where all nodes which are connected
via must-link constraints are merged into single nodes. We call this graph \emph{contracted graph}.
%
\begin{definition}\emph{(Contracted Graph)}
Given a weighted graph $G=V,E,w)$ segmentation of $G$ given by $y\in P(G)$,
we denote by $S: V \to \mathbb{N}$ a mapping from the nodes to the segments.
We define the contraction of graph $G_y=(V_y,E_y, \bar{w})$
by $V_y=\{S(v)|v\in V\}$, $E_y=\{S(u)S(v)|uv\in E\}$, and 
$\forall \bar{u}\bar{v}\in E_y: \bar{w}_{\bar{u}\bar{v}}=\sum_{uv\in E, S(u)=\bar{u},S(v)=\bar{v}}w_{uv}$ 
\end{definition}
%
Any clustering $\bar{y}$ of the contracted graph $G_y=(V_y,E_y)$ can be \emph{back projected} to a clustering $y$ the original graph $G=(V,E)$ by
%
\begin{align}
y_{uv}&=\left\{ 
\begin{array}{ll}
\bar{y}_{S(u)S(v)}& \textrm{ if }S(u) \neq S(v)\\
0                & \textrm{ else}
\end{array}
\right.& \forall uv \in E
\end{align}
Furthermore, the back projection of the optimal segmentation $\bar{y}$ of the contracted graph is a solution of problem~\ref{eq:fusion_move_a}.

% Eq.~\ref{eq:fusion_move_a} can be solved efficiently, since 
% we can work on a coarser graph, where all nodes which are connected
% via must-link constraints are merged into single nodes.
% This coarser graph is constructed by contracting all must-link edges
% (see Fig.~\ref{fig:move_graph}).

% \begin{definition}\emph{(Back Projection)}
% Given a segmentation $\bar{y}$ of a contradicted graph $G_y=(V_y,E_y)$.
% We define the back projection $\rho^G$ from $\bar{y}$ to a segmentation of original graph  $G=(V,E)$
% by 
% \begin{align}
% \rho^G_{uv}(\bar{y})=\left\{ 
% \begin{array}{ll}
% \bar{y}_{S(u)S(v)}& \textrm{ if }S(u) \neq S(v)\\
% 0                & \textrm{ else}
% \end{array}
% \right.
% \end{align}
% \end{definition}

\begin{theorem}[Equivalence]
The back projection of the optimal segmentation $\bar{y}^*$ of the contracted graph $G_y=(V_y,E_y, \bar{w})$
is an optimal solution of problem~\ref{eq:fusion_move_a}.
\begin{proof}
Let $y'$ be the back propagation of $\bar{y}^*$, which is by definition a feasible solution of~\ref{eq:fusion_move_a}.
If

Since $\bar{y}^*$ fulfills all-must link constraints of~\ref{eq:fusion_move_a} it is a feasible solution.
Let

, we have  $y^*\cdot w = \rho^{-1}_y(y^*)\cdot \bar{w}$.
Consequently, $y^*\cdot w = \rho_y(\bar{y}) \cdot w$ and  $\rho^{-1}_y(y^*)\cdot \bar{w}= \bar{y}\cdot\bar{w}$.
\end{proof}
%
\end{theorem}
